\documentclass{article}
\begin{document}
This is my \emph{first} document prepared in \LaTeX. I type it on \today.

We have seen that to typeset something in \LaTeX, we type in the text to be
together with some \LaTeX\ commands.
Words must be separated by spaces (does not matter how many)
and lines maybe broken arbitrarily.

\noindent The end of paragraph is specified by a \emph{blank line}
in the input. In other words, whenever you want to start a new
paragraph, just leave a blank line and proceed.

Carrots are good for your eyes, since they contain Vitamin A\@. Have
you ever seen a rabbit wearing glasses?

The numbers 1, 2, 3, etc.\ are called natural numbers. According to
Kronecker, they were made by God; all else being the works of Man.

I think \LaTeX\ is fun.

Note the difference in right and left quotes in \lq single quotes\rq\ and \lq\lq
 double quotes\rq\rq

X-rays are discussed in pages 221--225 of Volumn 3---the volume on electromagnetic
waves.

\'{E}l est\'{a} aqu\'{\i}

Maybe I have now learnt about 1\% of \LaTeX.

\noindent This is the first line.\\[10pt] This is the second line.

\begin{center}
{\bfseries\huge The \TeX nical Institute}\\[1cm]
{\scshape\LARGE Certificate}
\end{center}
\noindent This is to certify that Mr. N. O. Vice has undergone a course at this
institute and is qualified to be a \TeX nician.
\begin{flushright}
{\sffamily The Director\\
The \TeX nical Institue}
\end{flushright}

\textsf{\textbf{sans serif family, boldface series, uoright shape}}

\textrm{\textsl{roman family, medium series, slanted shape}}

\textit{A polygon of three sides is called a \emph{triangle} and a polygan of fo
ur sides is called a \emph{quadrilateral}}

\textbf{A polygon of three sides is called a \emph{triangle} and a polygan of fo
ur sides is called a \emph{quadrilateral}}

By a {\bfseries triangle}, we mean a polygon of three sides.

\end{document}
